Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-22 papers/ms.tex
update ms

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 11 were known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.  
This might however be an under-count,
since Kepler observed sparse 
regions of the complex, which are expected to have higher
contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}

@@

{\bf LGB TODO: add Tables}
Three tables:
1) All RSG-5 candidates (with rotation periods)
2) All CH-2 candidates (with rotation periods)
3) Cep-Her candidates observed by Kepler

>>>>

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this 
 yielded 11 known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.  
This might however be an under-count,
since Kepler observed sparse 
regions of the complex, which are expected to have higher
contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}

@@

{\bf LGB TODO: add Tables}
Three tables:
1) All RSG-5 candidates (with rotation periods)
2) All CH-2 candidates (with rotation periods)

Table~\ref{tab:cepherkepler} contains candidate Cep-Her members with
weights $\alpha>0.02$ observed by Kepler.  A cursory inspection of the
color absolute-magnitude diagram suggests that more restrictive weight
cuts would be needed to remove the majority of field star interlopers.
Table~\ref{tab:cepherkepler}  was created by cross-matching candidate
Cep-Her members (selected using Gaia EDR3;
Section~\ref{subsec:members}) against a Kepler to Gaia DR2 cross-match
(the \texttt{gaia-kepler.fun} crossmatch database created by Megan
Bedell).  The \texttt{kic_\dr2\_ang\_dist} column is from the latter
table.  The EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2_neighbourhood} table, and the closest (proper
motion and epoch-corrected) angular distance neighbor was taken as the
as single single match.  The \texttt{edr3\_dr2\_mag\_diff} column
gives some indication of the reliability of this EDR3 to DR2
conversion, as there are likely a few cases where partially resolved
binaries became fully resolved.

### 2022-04-22 papers/tab_supp_CepHer_X_Kepler.tex
update ms

%% Over-ride the default font size
%% Use Default (12pt)
\tabletypesize{\scriptsize}
%\tabletypesize{\small}

@@

%% This is the title of the table.
\tablecaption{Young, Age-dated, and Age-dateable Stars Within the
  Nearest Few Kiloparsecs.}
\label{tab:v06}

%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
%\tablenum{3}

@@

%% All data must appear between the \startdata and \enddata commands
%
% paste from
% /Users/luke/Dropbox/proj/rudolf/results/tables/v06_main_tableheader.tex
% via drivers/write_v06_main_tableheader.py
\startdata
          \texttt{source\_id} &                                          1709456705329541504 &                                              Gaia DR2 source identifier. \\
                  \texttt{ra} &                                                      247.826 &                                          Gaia DR2 right ascension [deg]. \\
                 \texttt{dec} &                                                       79.789 &                                              Gaia DR2 declination [deg]. \\
            \texttt{parallax} &                                                       35.345 &                                                 Gaia DR2 parallax [mas]. \\
     \texttt{parallax\_error} &                                                        0.028 &                                     Gaia DR2 parallax uncertainty [mas]. \\
                \texttt{pmra} &                                                       94.884 &      Gaia DR2 proper motion $\mu_\alpha \cos \delta$ [mas$\,$yr$^{-1}$]. \\
               \texttt{pmdec} &                                                      -86.971 &                  Gaia DR2 proper motion $\mu_\delta$ [mas$\,$yr$^{-1}$]. \\
  \texttt{phot\_g\_mean\_mag} &                                                         6.85 &                                                  Gaia DR2 $G$ magnitude. \\
 \texttt{phot\_bp\_mean\_mag} &                                                        6.409 &                                      Gaia DR2 $G_\mathrm{BP}$ magnitude. \\
 \texttt{phot\_rp\_mean\_mag} &                                                        7.189 &                                      Gaia DR2 $G_\mathrm{RP}$ magnitude. \\
             \texttt{cluster} &                  NASAExoArchive\_ps\_20210506,Uma,IR\_excess &                                   Comma-separated cluster or group name. \\
                 \texttt{age} &                                                 9.48,nan,nan &  Comma-separated logarithm (base-10) of reported$^{\rm a}$ age in years. \\
           \texttt{mean\_age} &                                                         9.48 &                           Mean (ignoring NaNs) of $\texttt{age}$ column. \\
       \texttt{reference\_id} &       NASAExoArchive\_ps\_20210506,Ujjwal2020,CottenSong2016 &                          Comma-separated provenance of group membership. \\
  \texttt{reference\_bibcode} &  2013PASP..125..989A,2020AJ....159..166U,2016ApJS..225...15C &                   ADS bibcode corresponding to $\texttt{reference\_id}$. \\
\enddata

@@

%% General table comment marker
\tablecomments{
Table~\ref{tab:v06} is published in its entirety in a machine-readable
format.   This table is a concatenation of the studies listed in
Table~\ref{tab:metadata}.  One entry is shown for guidance regarding
form and content.  In this particular example, the star has a cold
Jupiter on a 16 year orbit, HD 150706b \citep{2012AA...545A..55B}.  An
infrared excess has been reported \citep{CottenSong2016}, and the star
was identified by \citet{Ujjwal2020} as a candidate UMa moving group
member ($\approx 400\,{\rm Myr}$; \citealt{mann_tess_2020}).  The
star's RV activity and TESS rotation period corroborate its youth.
}
\vspace{-0.5cm}
\end{deluxetable*}

>>>>

%% Over-ride the default font size
%% Use Default (12pt)
%\tabletypesize{\scriptsize}
\tabletypesize{\small}

@@

%% This is the title of the table.
\tablecaption{Candidate Cep-Her members observed by Kepler}
\label{tab:cepherkepler}
%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
%\tablenum{3}

@@

%% All data must appear between the \startdata and \enddata commands
%
% paste from
% /Users/luke/Dropbox/proj/earhart/results/tables/NGC_2516_Prot_cleaned_header.tex
% via drivers/write_NGC2516_main_table.py
\startdata
\texttt{dr2\_source\_id}      & 2073765172933035008 & Gaia DR2 source identifier. \\
\texttt{dr3\_source\_id}      & 2073765172933035008 & Gaia (E)DR3 source identifier. \\
\texttt{kepid} & 5641711      & KIC identifier. \\
\texttt{ra} &    297.4099     & Gaia EDR3 right ascension [deg]. \\
\texttt{dec} &   40.8972      & Gaia EDR3 declination [deg]. \\
  \texttt{weight} & 0.0409    & Strength of the connectivity to other candidate cluster members. \\
  \texttt{v\_l} & -0.5061     & Longitudinal galactic velocity [km\,s$^{-1}$]. \\
  \texttt{v\_b} & -8.2328     & Latitudinal galactic velocity [km\,s$^{-1}$]. \\
  \texttt{x\_pc} & -8035.42&  & Galactocentric $X$ position coordinate [pc]. \\
  \texttt{y\_pc} & 331.44     & Galactocentric $Y$ position coordinate [pc]. \\
  \texttt{z\_pc} & 65.32      & Galactocentric $Z$ position coordinate [pc]. \\
  \texttt{kic\_dr2\_ang\_dist} & 0.298 & Separation between KIC and Gaia DR2 positions [arcsec]. \\
  \texttt{edr3\_dr2\_mag\_diff} & 0.002 & $G$-band difference between EDR3 and DR2 source match [mag]. \\
\enddata

@@

%% General table comment marker
\tablecomments{
Table~\ref{tab:cepherkepler} is published in its entirety in a machine-readable
format.  One entry is shown for guidance regarding form and content.
This involved a conversion based

is a concatenation of all candidate
NGC\,2516 members reported by \citetalias{cantatgaudin_gaia_2018},
\citetalias{kounkel_untangling_2019}, and \citetalias{meingast_2021}
based on the Gaia DR2 data.  Different levels of purity and
completeness can be achieved using different cuts on photometric
periods, periodogram powers, and lithium eqiuvalent widths.  Sets
$\mathcal{A}$ and $\mathcal{B}$ provide two possible levels of
cleaning (see Section~\ref{subsubsec:cluster}).  When the
target star is the only star present in the TESS aperture,
\texttt{nequal}$=0$, \texttt{nclose}$=1$, and \texttt{nfaint}$=1$.
The light curves are available at
\url{https://archive.stsci.edu/hlsp/cdips}.
Supplementary plots enabling analyses of individual stars
are available at \url{https://lgbouma.com/notes}.
}
\vspace{-0.5cm}
\end{deluxetable*}
